Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2024-09-12 Manuscript_Nater_etal.qmd
Updated model description to fit with new model structure

The initial densities, $D_{juv, x, j, 1}$ and $D_{ad, x, j, 1}$ are modelled for each site (= transect) as random realizations of log normal distributions with area-specific log means ($\mu^{D1}_x$) and log standard deviations ($\sigma^{D1}_x$). Survival ($S_{x,t}$) and recruitment ($R_{x,t}$), on the other hand, are assumed to be the same for all sites $j$ within a given area $x$ and were modelled as:

>>>>

The initial densities of adults, $D_{ad, x, j, 1}$, are modelled for each site (= transect) as random realizations of log normal distributions with area-specific log means ($\mu^{D1}_x$) and log standard deviations ($\sigma^{D1}_x$). Site-specific initial juvenile density, $D_{juv, x, j, 1}$, is calculated from initial adult density as $D_{ad, x, j, 1} * R_{x, 1}$. Survival ($S_{x,t}$) and recruitment ($R_{x,t}$), on the other hand, are assumed to be the same for all sites $j$ within a given area $x$ and were modelled as:
